Distribution Theory --- Example Sheet 2

### 2020-11-18 distribution_theory/distribution_ES2_handin.tex
opirseajf

\begin{proof}
	The convolution between $u, v \in \DD'(\RR^n)$ is defined by the formula
	\begin{equation} \label{def:convolution}
	(u * v) * \phi = u * (v * \phi) \quad\text{for all $\phi \in \DD(\RR^n)$}. 
	\end{equation}
Recall that for all $u \in \DD'(\RR^n) \phi\in \DD(\RR^n)$, we have $\ang{u, \phi} = (u * \refl\phi)(0)$, and therefore $u * v$ should satisfy
\[
\ang{u * v, \phi} = ((u * v) * \refl\phi)(0) = (u * (v * \refl\phi))(0) = \ang{u, \Rr(v * \refl\phi)}. 
\] Therefore 
\begin{enumerate}
	\item Define $w \colon \DD(\RR) \to \CC$ by 
	\[
	\ang{w, \phi} = \ang{u, \Rr(v * \refl\phi)}, 
	\]
	then we will show that $w$ satisfies $w * \phi = u * (v * \phi)$ for all $\phi \in \DD(\RR)$. 
	\begin{align*}
		(w * \phi)(x) &= \ang{w, \tau_x\refl\phi} = \ang{u, \Rr(v * \Rr(\tau_x \refl\phi))} = \ang{u, \Rr(v * \tau_{-x}\phi)} \\
		&= \ang{u, \Rr \tau_{-x} (v * \phi)} = \ang{u, \tau_x \Rr(v * \phi)} = (u * (v * \phi))(x). 
	\end{align*}
\item Uniqueness: we have shown in the lectures that if $w * \phi = w' * \phi$ for all $\phi$, then $w = w'$. This shows that \cref{def:convolution} uniquely defines $u * v$. 
\end{enumerate}
%	\[
%	\ang{u * v, \phi} = ((u * v) * \refl\phi)(0) = (u * (v * \refl\phi))(0),
%	\]
%	which shows that the formula \cref{def:convolution} uniquely defines $\ang{u * v, \phi}$ for any $\phi \in \DD(\RR^n)$, and therefore that $u * v$ is well-defined. For uniqueness,

@@

\begin{question}
	Show that if $u, v, w \in \DD'(\RR^n)$ and at least two of them have compact support, then the convolution is associative (i.e., $(u * v) * w) = u* (v * w)$). 
\end{question}

\begin{proof}
	Note that the convolution between two compactly supported distributions is again compactly supported, which ensures that both expressions `make sense'. Now, let $\phi \in \DD(\RR^n)$, then we have
	\begin{align*}
		((u * v) * w) * \phi &= (u* v) * (w * \phi) = u * (v * ( w* \phi)) = u * ((v * w) * \phi) = (u * (v * w)) * \phi,
	\end{align*}
	which proves the theorem. 
\end{proof}

\begin{question}
	Let $\phi \in \DD(\RR)$ and choose $\eps > 0$ sufficiently small so that $\supp(\phi) \subset I_\eps = (-1/\eps, 1/\eps)$. Given that $\phi$ has a uniformly convergent Fourier series on $I_\eps$ in the form
	\[
	\phi(x) = \sum_{n \in \ZZ} c_n e^{i \eps \pi n x}, \quad c_n = \frac\eps2 \int_\RR \phi(x) e^{-i\eps \pi n x} \dd{x},
	\]
	prove the Fourier inversion theorem on $\DD(\RR)$ by taking a suitable limit. 
\end{question}

\begin{proof}
Since $\DD(\RR) \subseteq \SS(\RR)$, we know that the Fourier inversion formula holds. We only need to show that the Fourier tranform of $\phi$ is again an element of $\DD(\RR)$. (??)
\end{proof}

\begin{question}
	For $\phi \in \SS(\RR^n)$ prove that $\sum_m \phi(m) = \sum_n \hat\phi(2\pi n)$. This is the famous Poisson summation formula. 
\end{question}

\begin{proof}
	We have
	\begin{align*}
		\sum_m \phi(m) = \frac1{(2\pi)^n} \sum_m \int e^{i\lambda m} \hat \phi(\lambda) \dd{\lambda} = \sum_m \int e^{2\pi i \lambda m} \hat \phi(2\pi \lambda) \dd{\lambda}
	\end{align*}
(??)
\end{proof}

\begin{question}
	If $u \in H^s(\RR^n)$ show that $D^\alpha u\in H^{s - \abs{\alpha}} (\RR^n)$. If $s > t$ show that $H^s(\RR^n) \subseteq H^t(\RR^n)$. 
\end{question}

\begin{proof}
	Assuming $u \in H^s(\RR^n)$, we have
	\begin{align*}
		\int_{\RR^n} \ang{\lambda}^{2(s - \abs{\alpha})} \abs{\widehat{D^\alpha u}(\lambda)}^2 \dd{\lambda}  &= \int_{\RR^n} \ang{\lambda}^{2(s-\abs{\alpha})} \norm{\lambda}^{2\abs{\alpha}} \abs{\hat u(\lambda)}^2 \dd{\lambda} \\
		&\les \int_{\RR^n} \ang{\lambda}^{2s} \abs{\hat u(\lambda)}^2 \dd{\lambda} < \infty, 
	\end{align*}
which proves $D^\alpha u \in H^{s- \abs{\alpha}}(\RR^n)$.

The second claim follows immediately from the fact that $\ang{\lambda}^{t} \leq \ang{\lambda}^s$ for $s \geq t$ and $\lambda$ sufficiently large. 
\end{proof}

\begin{question}
	Show that $S(\RR^n)$ is dense in $L^2(\RR^n) = H^0(\RR^n)$ and deduce that $\SS(\RR^n)$ is dense in $H^s(\RR^n)$.

	\emph{Hint:} Use Parseval's theorem. 
\end{question}

\begin{proof}
	We will show that $\DD(\RR^n)$ is dense in $L^2(\RR^n)$: since $\DD(\RR^n) \subseteq \SS(\RR^n)$, this shows that $\SS(\RR^n)$ is dense in $L^2(\RR^n)$ as well.

	(??)

	Now, for $u \in H^s(\RR^n)$, let $(\phi_m) \to u$ in $L^2$. Then we have
	\begin{align*}
		\norm{\phi_m - u}_{H^s}^2 = \int \ang{\lambda}^{2s} \abs{(\phi_m - u)(\lambda)}^2 \dd{\lambda}
	\end{align*}

(??)
\end{proof}

\begin{question}
	Prove that multiplication by a Schwarz function gives rise to a continuous map from $H^s(\RR^n)$ to itself, i.e., $\norm{\phi u}_{H^s} \les \norm{u}_{H^s}$ for $\phi \in \SS(\RR^n)$. You may assume Peetre's inequality: for $\lambda, \nu \in \RR^n$ and $s \in \RR$
	\[
	\qty(\frac{1 + \norm{\lambda}^2}{1 + \norm{\mu}^2})^s \leq 2^{\abs{s}} \qty(1 + \norm{\lambda - \mu}^2)^{\abs{s}}. 
	\]
\end{question}

\begin{proof}
	We have
	\begin{align*}
		\norm{\phi u}_{H^s}^2 &= \int \abs{\FF[\phi u](\lambda)}^2 (1 + \norm{\lambda})^2 \dd{\lambda}
	\end{align*}
(??) (how to bound fourier transform of product??)
\end{proof}
%-----------------------------------------------------------------------------
\setcounter{question}{18}

@@

	\item The derivative of this function, outside of 0, is $\log\abs{x}$.

>>>>

\begin{proof}
	The convolution between $u, v \in \DD'(\RR^n)$ is defined by the formula
	\begin{equation} \label{def:convolution}
	(u * v) * \phi = u * (v * \phi) \quad\text{for all $\phi \in \DD(\RR^n)$}. 
	\end{equation}
Recall that for all $u \in \DD'(\RR^n) \phi\in \DD(\RR^n)$, we have $\ang{u, \phi} = (u * \refl\phi)(0)$, and therefore $u * v$ should satisfy
\[
\ang{u * v, \phi} = ((u * v) * \refl\phi)(0) = (u * (v * \refl\phi))(0) = \ang{u, \Rr(v * \refl\phi)}. 
\] 
We can now show existence and uniqueness:
\begin{enumerate}
	\item Existence: define $w \colon \DD(\RR) \to \CC$ by 
	\[
	\ang{w, \phi} = \ang{u, \Rr(v * \refl\phi)}, 
	\]
	then we will show that $w$ satisfies $w * \phi = u * (v * \phi)$ for all $\phi \in \DD(\RR)$. 
	\begin{align*}
		(w * \phi)(x) &= \ang{w, \tau_x\refl\phi} = \ang{u, \Rr(v * \Rr(\tau_x \refl\phi))} = \ang{u, \Rr(v * \tau_{-x}\phi)} \\
		&= \ang{u, \Rr \tau_{-x} (v * \phi)} = \ang{u, \tau_x \Rr(v * \phi)} = (u * (v * \phi))(x). 
	\end{align*}
\item Uniqueness: we have shown in the lectures that if $w * \phi = w' * \phi$ for all $\phi$, then $w = w'$. This shows that \cref{def:convolution} uniquely defines $u * v$. 
\end{enumerate}
%	\[
%	\ang{u * v, \phi} = ((u * v) * \refl\phi)(0) = (u * (v * \refl\phi))(0),
%	\]
%	which shows that the formula \cref{def:convolution} uniquely defines $\ang{u * v, \phi}$ for any $\phi \in \DD(\RR^n)$, and therefore that $u * v$ is well-defined. For uniqueness,

@@

\setcounter{question}{18}

@@

	\item The derivative of this function is $\log(\abs{x})$, and the derivative of $\log(\abs{x})$ is $\PV(1/x)$ which we saw in the previous example sheet. By (a) we know that the Fourier transform of $\sign$ is $2i \PV(1/x)$, so we have
	\[
	\FF[2i \PV(1/x)] = \FF[\FF[\sign]] = (2\pi)^n \refl\sign \implies \FF[\PV(1/x)] = \frac{(2\pi)^n}{2i} \refl\sign.
	\]
	Note that $\refl\sign = -\sign$ we conclude
	\[
	\FF[x\log\abs{x}- x](\lambda) = \frac{(2\pi)^n}{2i\lambda^2} \sign(\lambda). 
	\]
